### 2018-02-15 Writing/Thesis/content/chapter-related-work.tex
working on tables + reworking related work chapter

\chapter{Related Work}
\label{sec:related}
% Of course much work in this field and cannot possibly cover all of this so confined to closely related or well-known / state of the art
The demand for aid in the process of selecting an algorithm has already led to the development of numerous solutions that automate machine-learning (AutoML). In the following sections, the workings of a few such tools that are related to this work are outlined briefly, loosely organized by their scope of operation. Each tool's usage of meta knowledge is discussed shortly.\\

\section{Predicting Rankings}
%% Ranking
% Incorporating times
In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifiers \cite{DBLP:journals/ml/AbdulrahmanBRV18}. They call this combined measure of accuracy and time A3R, and integrate it into two different ranking approaches. In both cases, the authors find that this leads to a better mean interval loss, which is a measure that expresses the mean loss experienced in respect to the time that has been allowed for the construction of the ranking, that is time taken to evaluate top-ranked classifiers.

% Rank aggregation A3R
One of those two approaches is called average-ranking. It utilizes meta knowledge to suggest a ranking of classifiers for a new data sets, which in this case consist of recorded past performances of classifiers on data sets. That means this algorithms aggregates the performances of classifiers on all rankings once and then always recommends the same ranking. The new measures is integrated here by, instead of ordering only according to performance values, the classifiers are ordered according to the combined measure A3R.

% Active testing A3R
The second approach does not initially use meta knowledge and is called active testing. Active testing is a strategy that 'intelligently select the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets. Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set. The authors aim to improve this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation, incorporating time in the estimations made by the strategy which previously only compared accuracy values.

\section{Algorithm and Hyperparameter Selection}
%% CASH
Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters are tools that in addition two selecting an algorithm also optimize its hyperparameters, which has been defined as 'the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}. Two widely used approaches of this kind are AUTO-WEKA and AUTO-SKLEARN. It has to be noted that thus these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.

% Auto-WEKA
Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}. It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka}, which also offers a user-friendly GUI in addition to a command-line interface and an API, to assist the large number of novice users of the software in selecting parameterized algorithms for their problems. The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}. In Auto-WEKA, the problem of selecting an algorithm and its hyperparameters is combined by treating the algorithm itself as a hyperparameter and searching the joint space of algorithms and hyperparameters for the best solution. An input data set is first preprocessed by means of feature selection. Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}. In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model. This cycle is then repeated until the allocated time has run out. Auto-WEKA exploits meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forest, which perform well on a large number of data sets, first. \\

@@

\section{Constructing pipelines}
%% Whole pipelines
Before a classifier is evaluated on a data set, often a number of pre-processing steps are executed first. These could include selecting promising features and discarding other and normalizing the data. The 'sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories' \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a machine learning pipeline. Two tools which construct such complete pipelines for data sets are MP-Plan and the RECIPE framework.

% ML-Plan
ML-Plan is an AutoML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}. This is achieved by viewing machine-learning as a task, building a hierarchical task network out of those tasks, and then searching for a solution in the induced tree structure. In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks. An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'. The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'build NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed. A best-first search algorithm in a modified variant is then used to find good solutions in this task network. For the actual implementation of the learning algorithms, WEKA is used. While this variant does not use meta-learning in the process of optimizing the pipeline, the authors find that their results exceed those achieved by Auto-WEKA.\\

@@

% Recipe framework
Similar to ML-PLAN, the RECIPE framework constructs whole classification pipelines for new problems \cite{DBLP:conf/eurogp/SaPOP17}. However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which 'is used to generate the initial population, as well as to constraint the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}. This means that generated individuals representing complete pipelines can never be invalid. So for a new data set combined with a grammar that represents the valid pipelines, the tool first initializes the first generation according to the grammar. The fitness of individuals is then evaluated by mapping them to their respective implementations in the scikit-learn framework, and a new generation is created that takes this newly gained information into account. Evaluation by the authors indicates that the RECIPE framework is able to compete with AUTO-SKLEARN and a different evolutionary approach, although it does not incorporate meta-knowledge in the search.

>>>>

\chapter{Related Work}
\label{sec:related}
% Of course much work in this field and cannot possibly cover all of this so confined to closely related or well-known / state of the art
The demand for aid in the process of selecting an algorithm has already led to the development of a number of solutions that automate machine-learning (AutoML). In the following sections, the functionality of a few such tools that are related to this work are outlined briefly, organized by their scope of operation. Each tool's usage of meta knowledge is discussed shortly.

\section{Predicting Rankings}
%% Ranking
% Incorporating times
In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifiers \cite{DBLP:journals/ml/AbdulrahmanBRV18}. They call this combined measure of accuracy and time A3R, and integrate it into two different ranking approaches. In both cases, the authors find that this leads to a better mean interval loss, which is a measure that expresses the mean loss experienced with respect to the time that has been allowed for the construction of the ranking, that is the time taken to evaluate top-ranked classifiers.

% Rank aggregation A3R
One of those two approaches is called average-ranking. It utilizes meta knowledge to suggest a ranking of classifiers for a new data set, which in this case consists of recorded past performances of classifiers on a number of data sets, meaning this algorithm aggregates the performances of classifiers across all data sets once and then always recommends the same ranking. The new measure is integrated here by, instead of ordering only according to performance values, ordering classifiers according to the combined measure A3R.

% Active testing A3R
The second approach does not initially use meta knowledge and is called active testing. Active testing is a strategy that 'intelligently selects the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets. Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set. The authors improved this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation variant, incorporating time in the estimations made by the strategy which previously only compared accuracy values.

\section{Algorithm and Hyperparameter Selection}
%% CASH
Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally also optimizing the classifier's hyperparameters, which has been defined as 'the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}. Two widely used approaches of this kind are Auto-WEKA and AUTO-SKLEARN. It has to be noted that thus these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.

% Auto-WEKA
Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}. It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka}, which also offers a user-friendly GUI in addition to a command-line interface and an API, to assist the large number of novice users of the software in selecting parametrized algorithms for their problems. The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}. In Auto-WEKA, the problem of selecting an algorithm and its hyperparameters is combined by treating the algorithm itself as a hyperparameter and searching the joint space of algorithms and hyperparameters for the best solution. An input data set is first preprocessed by means of feature selection. Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to 'iterate[...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}. In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model. This cycle is then repeated until the allocated time has run out. Auto-WEKA exploits hard-coded meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forest, which perform well on a large number of data sets, first. \\

@@

\section{Constructing pipelines}
%% Whole pipelines
Before a classifier is evaluated on a data set, often a number of pre-processing steps are executed first. This includes, for example, selecting promising features and discarding others, and normalizing the data. The 'sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories' \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a machine learning pipeline. Two tools which construct such complete pipelines for data sets are ML-Plan and the RECIPE framework.

% ML-Plan
ML-Plan is an AutoML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}. This is achieved by viewing machine-learning as a task, building a hierarchical task network out of the resulting subtasks, and then searching for a solution in the induced tree structure. In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks. An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'. The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'train NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed. A best-first search algorithm in a modified variant is then used to find good solutions in this task network. For the actual implementation of the learning algorithms, WEKA is used. Like Auto-WEKA, ML-Plan uses hard-coded meta-knowledge by using a fixed orders as to which classifiers are tried first. However, the authors find that their results exceed those achieved by Auto-WEKA.\\

@@

% Recipe framework
Similar to ML-PLAN, the RECIPE framework constructs whole classification pipelines for new problems \cite{DBLP:conf/eurogp/SaPOP17}. However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which 'is used to generate the initial population, as well as to constrain the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}. This means that generated individuals representing complete pipelines can never be invalid. So for a new data set combined with a grammar that represents the valid pipelines, the tool first initializes the first generation according to the grammar. The fitness of individuals is then evaluated by mapping them to their respective implementations in the scikit-learn framework, and a new generation is created that takes this newly gained information into account. Evaluation by the authors indicates that the RECIPE framework is able to compete with AUTO-SKLEARN and a different evolutionary approach, although it does not incorporate meta-knowledge in the search.
